Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-31 paper_comparison/paper_comparison/paper_comparison.Rmd
fill in conclusion

## Shape of non-linearity

@@

## Shape of heteroskedasticity

@@

## Effect of other fitted value distributions

### Fitted value distribution

The prediction in a regression model is $E(Y|X)$, that is, it is conditional on observed values of the predictors. The distribution of $X$, or consequently $\hat{Y}$, may however affect the ability to read any patterns in the residuals. <!-- Although the distribution of the regressor is classically not restricted by the assumptions of linear regression, it will have an impact on the fitted value distribution and the visual effect of the residual plot.--> The four distributions of fitted values, used in this experiment, were designed to examine this.

@@

For non-linearity patterns, we do not observe significant difference in power of visual test between distributions, except for the discrete uniform distribution. It is possibility due to the fact that humans have difficulties in recognising visual patterns from discreteness, which makes the shape disconnected and incomplete (ref?). In terms of conventional tests, the discrete uniform distribution is instead the one with the greatest power, followed by the lognormal distribution, the uniform distribution and the normal distribution.

@@

### Shape of non-linearity (old)

Shape of the non-linearity pattern is another factor contributed to the non-linearity model. According to Figure \ref{fig:poly-power-j}, conventional tests are significantly less powerful in testing "Triple-U" shape compared to other three shapes, though it is still more sensitive than the visual test. In fact, among the lineups containing non-linearity patterns used in our experiments, around `r vi_survey %>% filter(!attention_check) %>% filter(!null_lineup) %>% filter(type == "polynomial") %>% group_by(unique_lineup_id) %>% summarise(across(everything(), first)) %>% count(a = p_value < 0.05, b = conventional_p_value < 0.05) %>% mutate(prop = n / sum(n) * 100) %>% filter(a, !b) %>% pull(prop) %>% round(digits = 1)`% (two our of 576) are rejected by the visual test, but accepted by the conventional test.

Figure \ref{fig:poly-example} shows one of the two lineups where the visual test rejects the residual plot. The data plot, in position 18, is very obvious, and different from the nulls. The visual test is correct to reject. To understand why this is, one needs to return to the way the RESET test is applied. It requires a parameter indicating degree of fitted values to test for, and the recommendation is to generically use four (@ramsey_tests_1969). However, the "Triple-U" shape constructed from the Hermite polynomials use power up to 18. Both lineups rejected by the visual test but not the RESET are of "Triple-U". If the RESET test had been applied using the power up to six, all the decisions for these lineups would have been to reject. The recommendation of the polynomial power for the RESET should be revised, perhaps. This illustrates the sensitivity of conventional testing to the parameters, and it also points to a limitation that one needs to know the data structure in order to set the parameters for the test.

We expect the "U" shape will be the easiest one to be detected by subjects followed by the "S", "M" and "Triple-U" shape. From Figure \ref{fig:poly-power-j}, it can be observed that the power curves are mostly aligned with our expectation, except for the "M" shape. Interestingly, the "M" shape is as easy to be detected as the "U" shape. The readability of the shape do not strictly follow the degree of the polynomials.

```{r poly-power-j, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. Power curves with higher order of non-linearity are drawn with deeper colours."}

poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "polynomial") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>%
  select(shape, log_effect_size, reject, conv_or_not) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = shape), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(4, "TealGrn")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Non-linearity shape")
```

```{r poly-example, fig.height = 7, fig.width = 7, fig.cap = "Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel 18 exhibits strong non-linear pattern. It has effect size $= 3.96$. Interestingly, all the lineups in this group are higher order polynomials (Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!"}
# plot poly-275
VI_MODEL$plot_lineup(vi_lineup$poly_275$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

### Shape of heteroskedasticity (old)

We also investigate the impact of the shape of heteroskedasticity on the power of different tests. The corresponding result is presented in Figure \ref{fig:heter-power-a}. In theory, the "Left-triangle" and the "Right-triangle" should have little difference from the point of view of a Breusch-Pagan test. According to Figure \ref{fig:heter-power-a}, this is indeed the case. And these two shapes should have the same visual test power, unless the orientation of the visual pattern is a non-negligible factor from human perspective. However, by checking the bootstrap confidence intervals, it can be observed from Figure \ref{fig:heter-power-a} that when $3 < log(E) < 4$, the "Left-triangle" power curve is significantly greater than the "Right-triangle" power curve. This phenomenon is particularly interesting. It implies the current residual plot design is not robust to the orientation of the visual pattern, which is worth to be explored in future research.

```{r heter-power-a, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$."}

heter_conv_sim %>%
  filter(x_dist == "uniform") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(BP_p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Conventional") %>%
  bind_rows(vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(x_dist == "uniform", type == "heteroskedasticity") %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(reject = as.numeric(p_value < 0.05)) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(conv_or_not = "Visual")) %>%
  mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>%
  select(a, log_effect_size, reject, conv_or_not) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject, col = a), 
              se = FALSE, 
              method = "glm",
              method.args = list(family = binomial())) +

  # Draw bootstrap for Left-triangle
  geom_ribbon(data = ~get_boot_conf(filter(.x, 
                                           conv_or_not == "Visual", 
                                           a == "Left-triangle"),
                                    log_effect_size,
                                    reject,
                                    times = 1000) %>%
                mutate(conv_or_not = "Visual"),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rcartocolor::carto_pal(3, "Earth")[1],
              alpha = 0.2) +

  # Draw bootstrap for Right-triangle
  geom_ribbon(data = ~get_boot_conf(filter(.x, 
                                           conv_or_not == "Visual", 
                                           a == "Right-triangle"),
                                    log_effect_size,
                                    reject,
                                    times = 1000) %>%
                mutate(conv_or_not = "Visual"),
              aes(x = log_effect_size, 
                  ymin = lower, 
                  ymax = upper),
              fill = rcartocolor::carto_pal(3, "Earth")[3],
              alpha = 0.2) +

  # Theme
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  scale_color_manual(values = rcartocolor::carto_pal(3, "Earth")) +
  theme_light() +
  theme(legend.position = "bottom") +
  facet_wrap(~conv_or_not) +
  labs(col = "Heteroskedasticity shape")
```

@@

>>>>

## Effect of shape of non-linearity

@@

## Effect of shape of heteroskedasticity

@@

## Effect of fitted value distributions

The prediction in a regression model is $E(Y|X)$, that is, it is conditional on observed values of the predictors. The distribution of $X$, or consequently $\hat{Y}$, may however affect the ability to read any patterns in the residuals. The four distributions of fitted values, used in this experiment, were designed to examine this.

@@

For non-linearity patterns, we do not observe significant difference in power of visual test between distributions, except for the discrete uniform distribution. It could be due to the fact that humans have difficulties in recognising visual patterns from discreteness, which makes the shape disconnected and incomplete (ref?). In terms of conventional tests, the discrete uniform distribution is instead the one with the greatest power, followed by the lognormal distribution, the uniform distribution and the normal distribution.

@@

<!-- ### Shape of non-linearity (old) -->

<!-- Shape of the non-linearity pattern is another factor contributed to the non-linearity model. According to Figure \ref{fig:poly-power-j}, conventional tests are significantly less powerful in testing "Triple-U" shape compared to other three shapes, though it is still more sensitive than the visual test. In fact, among the lineups containing non-linearity patterns used in our experiments, around `r vi_survey %>% filter(!attention_check) %>% filter(!null_lineup) %>% filter(type == "polynomial") %>% group_by(unique_lineup_id) %>% summarise(across(everything(), first)) %>% count(a = p_value < 0.05, b = conventional_p_value < 0.05) %>% mutate(prop = n / sum(n) * 100) %>% filter(a, !b) %>% pull(prop) %>% round(digits = 1)`% (two our of 576) are rejected by the visual test, but accepted by the conventional test. -->

<!-- Figure \ref{fig:poly-example} shows one of the two lineups where the visual test rejects the residual plot. The data plot, in position 18, is very obvious, and different from the nulls. The visual test is correct to reject. To understand why this is, one needs to return to the way the RESET test is applied. It requires a parameter indicating degree of fitted values to test for, and the recommendation is to generically use four (@ramsey_tests_1969). However, the "Triple-U" shape constructed from the Hermite polynomials use power up to 18. Both lineups rejected by the visual test but not the RESET are of "Triple-U". If the RESET test had been applied using the power up to six, all the decisions for these lineups would have been to reject. The recommendation of the polynomial power for the RESET should be revised, perhaps. This illustrates the sensitivity of conventional testing to the parameters, and it also points to a limitation that one needs to know the data structure in order to set the parameters for the test. -->

<!-- We expect the "U" shape will be the easiest one to be detected by subjects followed by the "S", "M" and "Triple-U" shape. From Figure \ref{fig:poly-power-j}, it can be observed that the power curves are mostly aligned with our expectation, except for the "M" shape. Interestingly, the "M" shape is as easy to be detected as the "U" shape. The readability of the shape do not strictly follow the degree of the polynomials. -->

<!-- ```{r poly-power-j, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. Power curves with higher order of non-linearity are drawn with deeper colours."} -->

<!-- poly_conv_sim %>% -->
<!--   filter(x_dist == "uniform") %>% -->
<!--   mutate(log_effect_size = log(effect_size)) %>% -->
<!--   mutate(reject = as.numeric(RESET4_p_value < 0.05)) %>% -->
<!--   mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>% -->
<!--   mutate(conv_or_not = "Conventional") %>% -->
<!--   bind_rows(vi_survey %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(x_dist == "uniform", type == "polynomial") %>% -->
<!--   mutate(log_effect_size = log(effect_size)) %>% -->
<!--   mutate(reject = as.numeric(p_value < 0.05)) %>% -->
<!--   mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>% -->
<!--   mutate(conv_or_not = "Visual")) %>% -->
<!--   mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>% -->
<!--   select(shape, log_effect_size, reject, conv_or_not) %>% -->
<!--   ggplot() + -->
<!--   geom_smooth(aes(log_effect_size, reject, col = shape),  -->
<!--               se = FALSE,  -->
<!--               method = "glm", -->
<!--               method.args = list(family = binomial())) + -->
<!--   xlab(expression(log[e] (Effect_size))) + -->
<!--   ylab("Power") + -->
<!--   scale_color_manual(values = rcartocolor::carto_pal(4, "TealGrn")) + -->
<!--   theme_light() + -->
<!--   theme(legend.position = "bottom") + -->
<!--   facet_wrap(~conv_or_not) + -->
<!--   labs(col = "Non-linearity shape") -->
<!-- ``` -->

<!-- ```{r poly-example, fig.height = 7, fig.width = 7, fig.cap = "Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel 18 exhibits strong non-linear pattern. It has effect size $= 3.96$. Interestingly, all the lineups in this group are higher order polynomials (Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!"} -->
<!-- # plot poly-275 -->
<!-- VI_MODEL$plot_lineup(vi_lineup$poly_275$data,  -->
<!--                      remove_grid_line = TRUE,  -->
<!--                      theme = theme_light(), -->
<!--                      remove_axis = TRUE) -->
<!-- ``` -->

<!-- ### Shape of heteroskedasticity (old) -->

<!-- We also investigate the impact of the shape of heteroskedasticity on the power of different tests. The corresponding result is presented in Figure \ref{fig:heter-power-a}. In theory, the "Left-triangle" and the "Right-triangle" should have little difference from the point of view of a Breusch-Pagan test. According to Figure \ref{fig:heter-power-a}, this is indeed the case. And these two shapes should have the same visual test power, unless the orientation of the visual pattern is a non-negligible factor from human perspective. However, by checking the bootstrap confidence intervals, it can be observed from Figure \ref{fig:heter-power-a} that when $3 < log(E) < 4$, the "Left-triangle" power curve is significantly greater than the "Right-triangle" power curve. This phenomenon is particularly interesting. It implies the current residual plot design is not robust to the orientation of the visual pattern, which is worth to be explored in future research.  -->

<!-- ```{r heter-power-a, fig.height = 4, fig.cap = "Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$."} -->

<!-- heter_conv_sim %>% -->
<!--   filter(x_dist == "uniform") %>% -->
<!--   mutate(log_effect_size = log(effect_size)) %>% -->
<!--   mutate(reject = as.numeric(BP_p_value < 0.05)) %>% -->
<!--   mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>% -->
<!--   mutate(conv_or_not = "Conventional") %>% -->
<!--   bind_rows(vi_survey %>% -->
<!--   filter(!attention_check) %>% -->
<!--   filter(!null_lineup) %>% -->
<!--   filter(x_dist == "uniform", type == "heteroskedasticity") %>% -->
<!--   mutate(log_effect_size = log(effect_size)) %>% -->
<!--   mutate(reject = as.numeric(p_value < 0.05)) %>% -->
<!--   mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>% -->
<!--   mutate(conv_or_not = "Visual")) %>% -->
<!--   mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>% -->
<!--   select(a, log_effect_size, reject, conv_or_not) %>% -->
<!--   ggplot() + -->
<!--   geom_smooth(aes(log_effect_size, reject, col = a),  -->
<!--               se = FALSE,  -->
<!--               method = "glm", -->
<!--               method.args = list(family = binomial())) + -->

<!--   # Draw bootstrap for Left-triangle -->
<!--   geom_ribbon(data = ~get_boot_conf(filter(.x,  -->
<!--                                            conv_or_not == "Visual",  -->
<!--                                            a == "Left-triangle"), -->
<!--                                     log_effect_size, -->
<!--                                     reject, -->
<!--                                     times = 1000) %>% -->
<!--                 mutate(conv_or_not = "Visual"), -->
<!--               aes(x = log_effect_size,  -->
<!--                   ymin = lower,  -->
<!--                   ymax = upper), -->
<!--               fill = rcartocolor::carto_pal(3, "Earth")[1], -->
<!--               alpha = 0.2) + -->

<!--   # Draw bootstrap for Right-triangle -->
<!--   geom_ribbon(data = ~get_boot_conf(filter(.x,  -->
<!--                                            conv_or_not == "Visual",  -->
<!--                                            a == "Right-triangle"), -->
<!--                                     log_effect_size, -->
<!--                                     reject, -->
<!--                                     times = 1000) %>% -->
<!--                 mutate(conv_or_not = "Visual"), -->
<!--               aes(x = log_effect_size,  -->
<!--                   ymin = lower,  -->
<!--                   ymax = upper), -->
<!--               fill = rcartocolor::carto_pal(3, "Earth")[3], -->
<!--               alpha = 0.2) + -->

<!--   # Theme -->
<!--   xlab(expression(log[e] (Effect_size))) + -->
<!--   ylab("Power") + -->
<!--   scale_color_manual(values = rcartocolor::carto_pal(3, "Earth")) + -->
<!--   theme_light() + -->
<!--   theme(legend.position = "bottom") + -->
<!--   facet_wrap(~conv_or_not) + -->
<!--   labs(col = "Heteroskedasticity shape") -->
<!-- ``` -->

@@

This paper has demonstrated that conventional residual-based statistical tests are more sensitive to departures from assumptions for residuals than visual tests evaluated by humans in the diagnostics of linear regression models. Three experiments are conducted with two simulation models designed for non-linearity and heteroskedasticity model defects being applied. Methods for obtaining the $p$-value of visual tests proposed by @vanderplas2021statistical are extended to allowed for multiple selections in a lineup protocol.

Residual plots rejected by visual tests are rarely not rejected by conventional tests. Throughout the three human subject experiments we conducted, departures of residuals that are of little practical sense to humans will often be alarmed by conventional tests, supporting the common guidance given by experts to utilize graphical representations of data in model diagnostics.

Conventional tests relying on

such as RESET test

### 2023-01-31 paper_comparison/paper_comparison/paper_comparison.tex
fill in conclusion

\hypertarget{shape-of-non-linearity}{%
\subsection{Shape of non-linearity}\label{shape-of-non-linearity}}

@@

\hypertarget{shape-of-heteroskedasticity}{%
\subsection{Shape of
heteroskedasticity}\label{shape-of-heteroskedasticity}}

@@

\hypertarget{effect-of-other-fitted-value-distributions}{%
\subsection{Effect of other fitted value
distributions}\label{effect-of-other-fitted-value-distributions}}

\hypertarget{fitted-value-distribution}{%
\subsubsection{Fitted value
distribution}\label{fitted-value-distribution}}

@@

\hypertarget{shape-of-non-linearity-old}{%
\subsubsection{Shape of non-linearity
(old)}\label{shape-of-non-linearity-old}}

Shape of the non-linearity pattern is another factor contributed to the
non-linearity model. According to Figure \ref{fig:poly-power-j},
conventional tests are significantly less powerful in testing
``Triple-U'' shape compared to other three shapes, though it is still
more sensitive than the visual test. In fact, among the lineups
containing non-linearity patterns used in our experiments, around 0.3\%
(two our of 576) are rejected by the visual test, but accepted by the
conventional test.

Figure \ref{fig:poly-example} shows one of the two lineups where the
visual test rejects the residual plot. The data plot, in position 18, is
very obvious, and different from the nulls. The visual test is correct
to reject. To understand why this is, one needs to return to the way the
RESET test is applied. It requires a parameter indicating degree of
fitted values to test for, and the recommendation is to generically use
four (\citet{ramsey_tests_1969}). However, the ``Triple-U'' shape
constructed from the Hermite polynomials use power up to 18. Both
lineups rejected by the visual test but not the RESET are of
``Triple-U''. If the RESET test had been applied using the power up to
six, all the decisions for these lineups would have been to reject. The
recommendation of the polynomial power for the RESET should be revised,
perhaps. This illustrates the sensitivity of conventional testing to the
parameters, and it also points to a limitation that one needs to know
the data structure in order to set the parameters for the test.

We expect the ``U'' shape will be the easiest one to be detected by
subjects followed by the ``S'', ``M'' and ``Triple-U'' shape. From
Figure \ref{fig:poly-power-j}, it can be observed that the power curves
are mostly aligned with our expectation, except for the ``M'' shape.
Interestingly, the ``M'' shape is as easy to be detected as the ``U''
shape. The readability of the shape do not strictly follow the degree of
the polynomials.

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/poly-power-j-1}

\caption{Power of conventional tests and visual tests on lineups containing four different non-linearity shapes. Power curves with higher order of non-linearity are drawn with deeper colours.}\label{fig:poly-power-j}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/poly-example-1}

\caption{Example of a non-linearity that is rejected by the visual test but not by the RESET test. The data plot at panel 18 exhibits strong non-linear pattern. It has effect size $= 3.96$. Interestingly, all the lineups in this group are higher order polynomials (Triple-U), and it is apparent that the default RESET test under-performs. The RESET test using the higher order polynomial parameter could be used, but this would change it's performance for lower order polynomials. The only way for it to be sensitive to these type of departure is to know the order prior to testing!}\label{fig:poly-example}
\end{figure}

\hypertarget{shape-of-heteroskedasticity-old}{%
\subsubsection{Shape of heteroskedasticity
(old)}\label{shape-of-heteroskedasticity-old}}

We also investigate the impact of the shape of heteroskedasticity on the
power of different tests. The corresponding result is presented in
Figure \ref{fig:heter-power-a}. In theory, the ``Left-triangle'' and the
``Right-triangle'' should have little difference from the point of view
of a Breusch-Pagan test. According to Figure \ref{fig:heter-power-a},
this is indeed the case. And these two shapes should have the same
visual test power, unless the orientation of the visual pattern is a
non-negligible factor from human perspective. However, by checking the
bootstrap confidence intervals, it can be observed from Figure
\ref{fig:heter-power-a} that when \(3 < log(E) < 4\), the
``Left-triangle'' power curve is significantly greater than the
``Right-triangle'' power curve. This phenomenon is particularly
interesting. It implies the current residual plot design is not robust
to the orientation of the visual pattern, which is worth to be explored
in future research.

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/heter-power-a-1}

\caption{Power of conventional tests and visual tests on lineups produced by the heteroskedasticity model with three different shapes controlled by the parameter $a$.}\label{fig:heter-power-a}
\end{figure}

@@

>>>>

\hypertarget{effect-of-shape-of-non-linearity}{%
\subsection{Effect of shape of
non-linearity}\label{effect-of-shape-of-non-linearity}}

@@

\hypertarget{effect-of-shape-of-heteroskedasticity}{%
\subsection{Effect of shape of
heteroskedasticity}\label{effect-of-shape-of-heteroskedasticity}}

@@

\hypertarget{effect-of-fitted-value-distributions}{%
\subsection{Effect of fitted value
distributions}\label{effect-of-fitted-value-distributions}}

@@

@@

This paper has demonstrated that conventional residual-based statistical
tests are more sensitive to departures from assumptions for residuals
than visual tests evaluated by humans in the diagnostics of linear
regression models. Three experiments are conducted with two simulation
models designed for non-linearity and heteroskedasticity model defects
being applied. Methods for obtaining the \(p\)-value of visual tests
proposed by \citet{vanderplas2021statistical} are extended to allowed
for multiple selections in a lineup protocol.

Residual plots rejected by visual tests are rarely not rejected by
conventional tests. Throughout the three human subject experiments we
conducted, departures of residuals that are of little practical sense to
humans will often be alarmed by conventional tests, supporting the
common guidance given by experts to utilize graphical representations of
data in model diagnostics.

Conventional tests relying on

such as RESET test
